Taking Linear Logic Apart

### 2018-04-27 doc/tlla2018/main.tex
Fixed results of erroneous merge

  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
  to the process $\tm{Q}$ in a single step.
  The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
  $\Longrightarrow$.
  Reductions can only be constructed as follows:

@@

\begin{definition}[Reduction]\label{def:hcp-reduction}
 Reductions are described by the smallest relation $\Longrightarrow$ on process terms closed under rules in \cref{fig:hcp-reduction}.
%  A reduction $\reducesto{P}{Q}$ denotes that the process $\tm{P}$ can reduce
%  to the process $\tm{Q}$ in a single step.
%  The relation $\Longrightarrow^\star$ is the reflexive, transitive closure of
%  $\Longrightarrow$.
%  Reductions can only be constructed as follows:
\end{definition}

@@

\begin{definition}[Typing judgements]\label{def:hcp}
  A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes
  that the process $\tm{P}$ consists of $n$ independent, but potentially
  entangled processes, each of which communicates according to its own
  protocol $\Gamma_i$.
  Typing judgements can be constructed using the following inference rules.
  Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}$.
  \\[0.5\baselineskip]
  Structural Rules.
  \begin{center}\hccpInfAx        \hccpInfCycle\end{center}\vspace*{0.5\baselineskip}
  \begin{center}\hccpInfMix       \hccpInfHalt \end{center}\vspace*{0.5\baselineskip}

@@

\begin{lemma}[Preservation for $\equiv$]\label{lem:hcp-preservation-equiv}
  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal G}$.
\end{lemma}
\begin{proof}
  By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
\end{proof}

\begin{theorem}[Preservation]\label{thm:hcp-preservation}
  If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal G}$.
\end{theorem}
\begin{proof}
  By induction on the derivation of $\reducesto{P}{Q}$.
\end{proof}

>>>>

  Reductions are described by the smallest relation $\Longrightarrow$ on process
  terms closed under rules in \cref{fig:hcp-reduction}.

@@

@@

\begin{definition}[Typing judgements]\label{def:hcp}
  A typing judgement $\seq[P]{\Gamma_1 \hsep \dots \hsep \Gamma_n}$ denotes
  that the process $\tm{P}$ consists of $n$ independent, but potentially
  entangled processes, each of which communicates according to its own
  protocol $\Gamma_i$.
  Typing judgements can be constructed using the following inference rules.
  Each logical rule has the side condition that $\tm{x} \not\in \ty{\mathcal{G}}$.
  \\[0.5\baselineskip]
  Structural Rules.
  \begin{center}\hccpInfAx        \hccpInfCycle\end{center}\vspace*{0.5\baselineskip}
  \begin{center}\hccpInfMix       \hccpInfHalt \end{center}\vspace*{0.5\baselineskip}

@@

\begin{lemma}[Preservation for $\equiv$]\label{lem:hcp-preservation-equiv}
  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal{G}}$.
\end{lemma}
\begin{proof}
  By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
\end{proof}

\begin{theorem}[Preservation]\label{thm:hcp-preservation}
  If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal{G}}$.
\end{theorem}
\begin{proof}
  By induction on the derivation of $\reducesto{P}{Q}$.
\end{proof}
